Title

### 2023-05-08 main.tex
.

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\DeclareMathOperator{\tr}{tr}

@@

To design the circuit, we remember that a Pauli channel as the one in
eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: citcuit-pauli-1},
 which is a special case of fig. \ref{fig: circuit-pauli}
 but with all details \cpnote{y compuertas , etc digamos que details}\tbnote{Va, listo} explicitly shown.

\begin{figure}[h!]
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
 decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
reducir a sólo uno}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).
Here we have two ancilla qubits, and the state 
$b_{00} |00\rangle + b_{01} |01\rangle + b_{10} |10\rangle + b_{11}|11\rangle$ 
is created on them with the help of three rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) - \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, 
$ \theta_1 = 2 \arccos(\sqrt{k_{00} + k_{01}})$ and
$ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit,
Chuang:1996} to obtain the {\color{red} Choi matrix} {\color{orange} operator $\xi_I$}  corresponding to the implementation of
the circuit {\color{red} $\mathcal{C}_{I}$} .
Then, we compared this {\color{red} Choi matrix} {\color{orange} operator} with the theoretical
{\color{red} Choi matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} 
of the channel we wanted to implement.
\cpnote{Quizá referirnos mejor al canal? Lo discutimos.} 
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

@@

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}
% }}}
\section{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
% }}}
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

@@

% }}}
\newpage
\appendix
\input{Cosas-Escritas-Antes}

>>>>

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\DeclareMathOperator{\tr}{tr}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

@@

To design the circuit, we remember that a Pauli channel as the one in
eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state0}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
 which is a special case of fig. \ref{fig: circuit-pauli}
 but with all details \cpnote{y compuertas , etc digamos que details}\tbnote{Va, listo} explicitly shown.

\begin{figure}[h!]
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
 decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
reducir a sólo uno}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).
Here we have two ancilla qubits, and the state 
$b_{00} |00\rangle + b_{01} |01\rangle + b_{10} |10\rangle + b_{11}|11\rangle$ 
is created on them with the help of three rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) - \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, 
$ \theta_1 = 2 \arccos(\sqrt{k_{00} + k_{01}})$ and
$ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
\label{fig: circuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit,
Chuang:1996} to obtain the {\color{red} Choi matrix} {\color{orange} operator $\xi_I$}  corresponding to the implementation of
the circuit {\color{red} $\mathcal{C}_{I}$} .
Then, we compared this {\color{red} Choi matrix} {\color{orange} operator} with the theoretical
{\color{red} Choi matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} 
of the channel we wanted to implement.
\cpnote{Quizá referirnos mejor al canal? Lo discutimos.} 
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

@@

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in eq. (\ref{eq: parametrized state}).

In general, producing this curve of states will require multiple rotations
parametrized by $p$. For instance, in the case of a two-qubit curve of states,
we would typically need three rotations that depend on $p$, s
imilar to those illustrated for the ancilla qubits in fig. (\ref{fig: circuit-pauli-1}).
Moreover, creating an $N$-qubit curve of states
usually necessitates $N-1$ parametrized rotations.

However, it is desirable to minimize the number of parametrized rotations in our circuit.
This leads us to the following question: which curves of states,
such as the one described in eq. (\ref{eq: parametrized state}), 
can be generated using only a single parametrized rotation? 
To clarify this, we provide the following definition for a circuit with one parametrized rotation.

\begin{definition}{\textbf{OPR Circuit:}}
An OPR (One-Parameterized Rotation) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}

Based on this definition, we aim to determine which curves of 
states can be generated using OPR circuits. 
To accomplish this, we begin by proving that any OPR circuit exhibits 
a specific form, as stated in the following theorem.

\begin{theorem}
An $N-$qubit OPR circuit can always be transformed into the form shown in
fig.~(\ref{fig:OPR-circuit}).
\end{theorem}

\begin{figure}[h!]
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of an OPR circuit}.
Any OPR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter}
\label{fig:OPR-circuit}
\end{figure}

\textbf{Proof:} 
First, we observe that according to the
definition, an OPR circuit always consists of an operation $B$ followed 
by the parametrized rotation and then another operation $A$, 
where $A$ and $B$ are not parametrized.

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any OPR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the target qubit for the rotation.

Therefore, an OPR circuit can be transformed such
that the rotation is around $\sigma_3$ and is applied to the last qubit 
(possibly controlled by other qubits), 
resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). $\blacksquare$ \\
$\;$\\

With the aid of this theorem, we can now determine the curves
of states of $N$ qubits that can be generated using an OPR circuit. 
This result is stated in the following theorem.

\begin{theorem}
An OPR circuit always implements an operator whose matrix,
in the computational basis, has the form:
\begin{eqnarray}
U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
\end{eqnarray}
where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
Using Theorem 1, we know that any OPR circuit can be transformed into the 
form shown in Figure (\ref{fig:OPR-circuit}).
Hence, we only need to consider the operator corresponding to that circuit. 
The $j$-th column of the circuit's matrix represents the result of applying the circuit to the state $|j\rangle$.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$.
This can be rewritten by separating the
first $N-1$ qubits from the last one as:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
\end{equation}
After the operator $B$, the circuit applies a controlled rotation to the last qubit.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions 
(which we denote as the set $C$)
and those that do not.
Therefore, the state can be written as
\begin{eqnarray}
B|j\rangle = \sum_{k \in C} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in C} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
After $B$ creates this state, we need to apply the controlled rotation to the result. 
This rotation will only be applied for the states on the first sum (since they fulfill the control conditions)
and not to the others. Therefore, we apply the gate to the last qubit of the first sum, 
remembering that $R_z(2s)$ acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, and the result is:
\begin{small}
\begin{eqnarray}
&e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle 
+ \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
& \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{eqnarray}
\end{small}
where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
 These vectors are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$, 
which is unitary.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
\end{eqnarray}
where $\vec{a}_j = A \vec{a'}_j , \vec{b}_j = A \vec{b'}_j , \vec{c}_j = A \vec{c'}_j$ are still orthogonal
vectors that satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$ because $A$ is unitary. 
Therefore, we conclude that the circuit takes a state $|j\rangle$ and converts it
 into the state represented by the vector $\vec{v}_j$, which means that the matrix representation of the circuit's operation in the 
computational base is
 $U = (|\vec{v}_0|, |\vec{v}_1|, \cdots, |\vec{v}_{2^n-1}|)$. $\blacksquare$  \\
 $\;$ \\

Therefore, from this theorem we conclude that
the kind of curves of states that can be created
using an OPR circuit are always of the form
\begin{align*}
|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
\end{align*}
where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
\newpage
% }}}
\section{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
We can now use the last theorem to conclude directly which Pauli dynamical maps
can be created using an OPR circuit.
For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

We can see some examples of Pauli dynamical
maps of one qubit that can be implemented with an OPR circuit:
\begin{itemize}
\item \textbf{$\sigma_3$ parabolic map:} We take as an example the Pauli dynamical map for one qubit defined as
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. \\

To implement this dynamical map using the circuit presented in figure \ref{fig:OPR-circuit}, it is necessary to create the state
\begin{eqnarray}
\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
\end{eqnarray}
on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
\begin{eqnarray}
\begin{pmatrix}
1/2 \\
0 \\ 
0 \\
1/2
\end{pmatrix} + \begin{pmatrix}
0 \\
1/2 \\
1/2 \\
0
\end{pmatrix}  \cos s + \begin{pmatrix}
-1/2 \\
0 \\
0 \\
1/2
\end{pmatrix} \sin s
\end{eqnarray}
with $s = \arcsin p$. According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation. The circuit used will have the same form as that in figure , where the part used to create the state on the ancilla qubits will be:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
\end{quantikz}
\caption{Circuit to create 2-qubit state}
\end{figure}

where according to theorem 1, matrices $A$ and $B$ can be chosen as:
\begin{eqnarray}
A &= \begin{pmatrix}
*  & c_0 / \sqrt{1-r^2} & -b_0/r & a_0 /r \\
*  & c_1 / \sqrt{1-r^2} & -b_1/r & a_1 /r \\ 
* & c_2 / \sqrt{1-r^2} & -b_2/r & a_2/r \\
* & c_3 / \sqrt{1-r^2} & -b_3/r & a_3/r \\
\end{pmatrix} = \begin{pmatrix}
0 & 1/\sqrt{2} & -1/\sqrt{2} & 0 \\
-1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
0 & 1/\sqrt{2} & 1/\sqrt{2} & 0
\end{pmatrix} \\
B& = \begin{pmatrix}
0 & 0 & 0 & 1 \\
0 & 1 & 0 & 0\\
0 & 0& 1 & 0 \\
1 & 0 & 0 & 0 
\end{pmatrix}
\end{eqnarray}
\end{itemize}

%\textbf{Puntos:}
%\begin{itemize}
%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
%\end{itemize}
% }}}

\newpage
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

@@

% }}}
\newpage
\appendix
%\input{Cosas-Escritas-Antes}
